Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Proof-of-Concept VI}}

### 2014-12-06 Paper.tex
No minimum gas price.

\begin{description}
\item[parentHash] The Keccak 256-bit hash of the parent block, in its entirety; formally $H_p$.
\item[unclesHash] The Keccak 256-bit hash of the uncles list portion of this block; formally $H_u$.
\item[coinbase] The 160-bit address to which all fees collected from the successful mining of this block be transferred; formally $H_b$.
\item[stateRoot] The Keccak 256-bit hash of the root node of the state trie, after all transactions are executed and finalisations applied; formally $H_r$.
\item[transactionsTrie] The Keccak 256-bit hash of the root node of the trie structure populated with each transaction in the transactions list portion of the block; formally $H_t$.
\item[difficulty] A scalar value corresponding to the difficulty level of this block. This can be calculated from the previous block's difficulty level and the timestamp; formally $H_d$.
\item[number] A scalar value equal to the number of ancestor blocks. The genesis block has a number of zero; formally $H_i$.
\item[minGasPrice] A scalar value equal to the minimum price of gas a transaction must have provided in order to be sufficient for inclusion by this miner in this block; formally $H_m$.
\item[gasLimit] A scalar value equal to the current limit of gas expenditure per block; formally $H_l$.
\item[gasUsed] A scalar value equal to the total gas used in transactions in this block; formally $H_u$.
\item[timestamp] A scalar value equal to the reasonable output of Unix's time() at this block's inception; formally $H_s$.
\item[extraData] An arbitrary byte array containing data relevant to this block. With the exception of the genesis block, this must be 32 bytes or fewer; formally $H_x$.
\item[nonce] A 256-bit hash which proves that a sufficient amount of computation has been carried out on this block; formally $H_n$.
\end{description}

@@

The function $L_B$ and $L_H$ are the preparation functions for a block and block header respectively. Much like the transaction receipt preparation function $L_R$, we assert the types and order of the structure for when the RLP transformation is required:
\begin{eqnarray}
\quad L_H(H) & \equiv & (\begin{array}[t]{l}H_p, H_u, H_b, H_r, H_t, H_d,\\ H_i, H_m, H_l, H_u, H_s, H_x, H_n \; )\end{array} \\
\quad L_B(B) & \equiv & \big( L_H(B_H), L_R^*(B_\mathbf{R}), L_H^*(B_\mathbf{U}) \big)
\end{eqnarray}

@@

The component types are defined thus:
\begin{equation}
\begin{array}[t]{lclclcl}
H_p \in \mathbb{B}_{32} & \wedge & H_u \in \mathbb{B}_{32} & \wedge & H_b \in \mathbb{B}_{20} & \wedge \\
H_r \in \mathbb{B}_{32} & \wedge & H_t \in \mathbb{B}_{32} & \wedge & H_d \in \mathbb{P} & \wedge \\
H_i \in \mathbb{P} & \wedge & H_m \in \mathbb{P} & \wedge & H_l \in \mathbb{P} & \wedge \\
H_u \in \mathbb{P} & \wedge & H_s \in \mathbb{P} & \wedge & H_x \in \mathbb{B} & \wedge \\
H_n \in \mathbb{B}_{32} &&&&
\end{array}
\end{equation}

@@

The given \textbf{gasUsed} and \textbf{minGasPrice} must correspond faithfully to the transactions listed. In the case of ${B_H}_m$, the minimum gas price, all transactions included in the transaction receipt must have a gas price, ${T_0}_p$, that is at least this value:
\begin{equation}
\forall \; T \in B_\mathbf{T}: T_p \geq {B_H}_m
\end{equation}

In the case of ${B_H}_u$, the total gas used in the block, it must be equal to the accumulated gas used according to the final transaction:
\begin{equation}
{B_H}_u = \ell(\mathbf{R})_u
\end{equation}

>>>>

\begin{description}
\item[parentHash] The Keccak 256-bit hash of the parent block, in its entirety; formally $H_p$.
\item[unclesHash] The Keccak 256-bit hash of the uncles list portion of this block; formally $H_u$.
\item[coinbase] The 160-bit address to which all fees collected from the successful mining of this block be transferred; formally $H_b$.
\item[stateRoot] The Keccak 256-bit hash of the root node of the state trie, after all transactions are executed and finalisations applied; formally $H_r$.
\item[transactionsTrie] The Keccak 256-bit hash of the root node of the trie structure populated with each transaction in the transactions list portion of the block; formally $H_t$.
\item[difficulty] A scalar value corresponding to the difficulty level of this block. This can be calculated from the previous block's difficulty level and the timestamp; formally $H_d$.
\item[number] A scalar value equal to the number of ancestor blocks. The genesis block has a number of zero; formally $H_i$.
\item[gasLimit] A scalar value equal to the current limit of gas expenditure per block; formally $H_l$.
\item[gasUsed] A scalar value equal to the total gas used in transactions in this block; formally $H_u$.
\item[timestamp] A scalar value equal to the reasonable output of Unix's time() at this block's inception; formally $H_s$.
\item[extraData] An arbitrary byte array containing data relevant to this block. With the exception of the genesis block, this must be 32 bytes or fewer; formally $H_x$.
\item[nonce] A 256-bit hash which proves that a sufficient amount of computation has been carried out on this block; formally $H_n$.
\end{description}

@@

The function $L_B$ and $L_H$ are the preparation functions for a block and block header respectively. Much like the transaction receipt preparation function $L_R$, we assert the types and order of the structure for when the RLP transformation is required:
\begin{eqnarray}
\quad L_H(H) & \equiv & (\begin{array}[t]{l}H_p, H_u, H_b, H_r, H_t, H_d,\\ H_i, H_l, H_u, H_s, H_x, H_n \; )\end{array} \\
\quad L_B(B) & \equiv & \big( L_H(B_H), L_R^*(B_\mathbf{R}), L_H^*(B_\mathbf{U}) \big)
\end{eqnarray}

@@

The component types are defined thus:
\begin{equation}
\begin{array}[t]{lclclcl}
H_p \in \mathbb{B}_{32} & \wedge & H_u \in \mathbb{B}_{32} & \wedge & H_b \in \mathbb{B}_{20} & \wedge \\
H_r \in \mathbb{B}_{32} & \wedge & H_t \in \mathbb{B}_{32} & \wedge & H_d \in \mathbb{P} & \wedge \\
H_i \in \mathbb{P} & \wedge & H_u \in \mathbb{P} & \wedge & H_l \in \mathbb{P} & \wedge \\
H_s \in \mathbb{P} & \wedge & H_x \in \mathbb{B} & \wedge & H_n \in \mathbb{B}_{32}
\end{array}
\end{equation}

@@

The given \textbf{gasUsed} must correspond faithfully to the transactions listed: ${B_H}_u$, the total gas used in the block, must be equal to the accumulated gas used according to the final transaction:
\begin{equation}
{B_H}_u = \ell(\mathbf{R})_u
\end{equation}
